An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-14 paper.tex
Proofed conclusion.

A similar work flow was used to produce Figure~\ref{fig:angle-torque-comparison}
which compares the mean and standard deviation of saggital plane joint angles
and torques from the perturbed gait cycles and the unperturbed gait cycles
computed from trial 20. This gives an idea of the more highly variable dynamics
required to walk while being longitudinally perturbed.
%
\begin{figure}
  \centering
  \includegraphics{figures/unperturbed-perturbed-comparison.pdf}
  \cprotect\caption{Mean (right: solid, left: dashed) and $3\sigma$ (shaded)
    joint angles and torques from both unperturbed (purple) and perturbed
    (blue) gait cycles from trial 20. Produced by
    \verb|src/unperturbed_perturbed_comparison.py|.}
  \label{fig:angle-torque-comparison}
\end{figure}

@@

\section*{Conclusion}

We have presented the details of what we believe to be a rich dataset of motion
and ground reaction loads humans exhibit when recovering from minor
longitudinal perturbations. The data provides a large sample of gait cycles
from both unperturbed and perturbed walking at three different nominal speeds.
The raw data is provided for reuse with sufficient detail with regards to meta
data and technical details. In addition to the data, we provide software that
can process the data for cleaning purposes and to produce typical saggital
plane gait variables of interest. Among other uses, we believe the dataset is
ideally suited for control identification purposes. Many researchers are
working on mathematical models for control in gait and this dataset provides
both a way to validate these models and data that can be used to generate
models.

>>>>

A similar work flow was used to produce Figure~\ref{fig:angle-torque-comparison}
which compares the mean and standard deviation of sagittal plane joint angles
and torques from the perturbed gait cycles and the unperturbed gait cycles
computed from trial 20. This gives an idea of the more highly variable dynamics
required to walk while being longitudinally perturbed.
%
\begin{figure}
  \centering
  \includegraphics{figures/unperturbed-perturbed-comparison.pdf}
  \cprotect\caption{Mean (right: solid, left: dashed) and $3\sigma$ (shaded)
    joint angles and torques from both unperturbed (purple) and perturbed
    (blue) gait cycles from trial 20. Produced by
    \verb|src/unperturbed_perturbed_comparison.py|.}
  \label{fig:angle-torque-comparison}
\end{figure}

@@

\section*{Conclusion}
%
We have presented the details of what we believe to be a rich and elaborate
data set of motion and ground reaction loads humans exhibit during both normal
walking and when recovering from longitudinal perturbations. The data provides
a very large sample of gait cycles from both unperturbed and perturbed walking
at three different nominal speeds. The raw data is provided for reuse with
complete meta data. In addition to the data, we provide software that can
process the data for both cleaning purposes and to produce typical sagittal
plane gait variables of interest. The variation of these gait variables and
statistics are provided to give a high level picture of the character of the
data. Among other uses, we believe the dataset is ideally suited for control
identification purposes. Many researchers are working on mathematical models
for control in gait and this dataset provides both a way to validate these
models and a source for generating them.
